The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2024-03-11 r_r/submission/manuscript_rihe_r_r.Rmd
copy editing manuscript 3.10.24

For selective private universities, the number of visits to private high schools ranged from a low of `r events_df %>% filter(univ_id == '186867', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` by Stevens Institute of Technology to a high of `r events_df %>% filter(univ_id == '152080', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` by Notre Dame, with the median universities -- Boston College and Northwestern University -- visiting `r events_df %>% filter(univ_id == '164924', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` and `r events_df %>% filter(univ_id == '147767', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` private high schools, respectively. Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities. That said, several public research universities in our sample -- University of Colorado-Boulder (`r events_df %>% filter(univ_id == '126614', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), University of South Carolina (`r events_df %>% filter(univ_id == '218663', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), and University of Alabama  (`r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.

@@

Table \@ref(tab:privu-percent-matrix) shows overlap in private high schools visited by the selective private universities in our sample. Appendix Table \@ref(tab:privu-count-matrix) shows counts. The networks of private universities appear to have more overlap than the network of public research universities. This is demonstrated tabularly by the higher percentages in Table \@ref(tab:privu-percent-matrix) compared to Table \@ref(tab:pubu-percent-matrix). Private universities that share a high percentage of visits tend to have the same religious affiliation and/or be located in the same geographic region. For example, the Catholic universities -- Notre Dame, Villanova, Boston College, and Marquette -- seem to visit many private high schools in common.

>>>>

For selective private universities, the number of visits to private high schools ranged from a low of `r events_df %>% filter(univ_id == '186867', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` by Stevens Institute of Technology to a high of `r events_df %>% filter(univ_id == '152080', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` by Notre Dame, with the median universities -- Boston College and Northwestern University -- visiting `r events_df %>% filter(univ_id == '164924', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` and `r events_df %>% filter(univ_id == '147767', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` private high schools, respectively. Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities. That said, several public research universities in our sample -- CU-Boulder (`r events_df %>% filter(univ_id == '126614', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), University of South Carolina (`r events_df %>% filter(univ_id == '218663', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), and University of Alabama (`r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.

@@

Table \@ref(tab:privu-percent-matrix) shows overlap in private high schools visited by the selective private universities in our sample. Appendix Table \@ref(tab:privu-count-matrix) shows counts. The networks of private universities appear to have more overlap than the networks of public research universities. This is demonstrated tabularly by the higher percentages in Table \@ref(tab:privu-percent-matrix) compared to Table \@ref(tab:pubu-percent-matrix). Private universities that share a high percentage of visits tend to have the same religious affiliation and/or be located in the same geographic region. For example, the Catholic universities -- Notre Dame, Villanova, Boston College, and Marquette -- seem to visit many private high schools in common.

### 2024-03-11 r_r/submission/manuscript_rihe_r_r.tex
copy editing manuscript 3.10.24

For selective private universities, the number of visits to private high schools ranged from a low of 181 by Stevens Institute of Technology to a high of 723 by Notre Dame, with the median universities -- Boston College and Northwestern University -- visiting 349 and 390 private high schools, respectively. Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities. That said, several public research universities in our sample -- University of Colorado-Boulder (402 visits), University of South Carolina (498 visits), and University of Alabama (1,039 visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.

@@

Table \ref{tab:privu-percent-matrix} shows overlap in private high schools visited by the selective private universities in our sample. Appendix Table \ref{tab:privu-count-matrix} shows counts. The networks of private universities appear to have more overlap than the network of public research universities. This is demonstrated tabularly by the higher percentages in Table \ref{tab:privu-percent-matrix} compared to Table \ref{tab:pubu-percent-matrix}. Private universities that share a high percentage of visits tend to have the same religious affiliation and/or be located in the same geographic region. For example, the Catholic universities -- Notre Dame, Villanova, Boston College, and Marquette -- seem to visit many private high schools in common.

>>>>

For selective private universities, the number of visits to private high schools ranged from a low of 181 by Stevens Institute of Technology to a high of 723 by Notre Dame, with the median universities -- Boston College and Northwestern University -- visiting 349 and 390 private high schools, respectively. Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities. That said, several public research universities in our sample -- CU-Boulder (402 visits), University of South Carolina (498 visits), and University of Alabama (1,039 visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.

@@

Table \ref{tab:privu-percent-matrix} shows overlap in private high schools visited by the selective private universities in our sample. Appendix Table \ref{tab:privu-count-matrix} shows counts. The networks of private universities appear to have more overlap than the networks of public research universities. This is demonstrated tabularly by the higher percentages in Table \ref{tab:privu-percent-matrix} compared to Table \ref{tab:pubu-percent-matrix}. Private universities that share a high percentage of visits tend to have the same religious affiliation and/or be located in the same geographic region. For example, the Catholic universities -- Notre Dame, Villanova, Boston College, and Marquette -- seem to visit many private high schools in common.
